An algorithm for finding the global extremum of a partially defined function\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}

### 2023-08-27 2023/MMST/samplepaper.tex
add two references

\begin{document}
%
\title{An algorithm for finding the global extremum 
of a partially defined function\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Marina Usova\inst{1}\orcidID{0000-0002-0722-6884} \and
Konstantin Barkalov\inst{1}\orcidID{0000-0001-5273-2471}}
%
\authorrunning{M. Usova et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Department of Mathematical Software and Supercomputing Technologies, Lobachevsky University, 603022 Nizhni Novgorod, Russia
\email{\{usova,konstantin.barkalov\}@itmm.unn.ru}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper discusses the problem of finding the global minimum of a function that may be partially defined in the search domain. The objective function may not be defined within some search regions due to the nature of the optimized object and of the simulation method (for example, numerical instability of the simulation method used). In some cases, these regions are known; but in most cases, the information about them is missing. The paper gives a description of a global search algorithm for solving such class of problems. Numerical experiments confirming the efficiency of the proposed algorithm were carried out.

\keywords{Lipschitz global optimization \and multiextremal functions \and hidden constraints \and dimensionality reduction.}
\end{abstract}
%
%
%
\section{Introduction}
Global optimization [...rus...] problems of finding the global (absolute) minima of multidimensional multiextremal functions. The possibility of building a reliable estimate of the global extremum in such problems is based principally on the availability of the \textit{a priori} known information on the problem to be solved allowing relating the possible values of the objective function to the known values in the points of search trials performed.

@@

Note that the use of complex mathematical models is natural in the optimization of complex real world objects that, as a consequence, increases the computation costs for searching the optimum Essentially. In last decades, the experts in the fields of optimization and parallel computations have proposed many methods for reducing the computation costs an speed-up of the algorithms related to solving the optimization problems appearing as well as to the numerical analysis of the original models [...ref???...].

>>>>

\begin{document}
%
\title{An algorithm for finding the global extremum 
of a partially defined function\thanks{This work was supported by the Russian Science Foundation, project No. 21-11-00204.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Marina Usova\inst{1}\orcidID{0000-0002-0722-6884} \and
Konstantin Barkalov\inst{1}\orcidID{0000-0001-5273-2471}}
%
\authorrunning{M. Usova et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{
Department of Mathematical Software and Supercomputing Technologies, Lobachevsky University, 603022 Nizhni Novgorod, Russia
\email{\{usova,konstantin.barkalov\}@itmm.unn.ru}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
The paper discusses the problem of finding the global minimum of a function that may be partially defined in the search domain. The objective function may not be defined within some search regions due to the nature of the optimized object and of the simulation method (for example, numerical instability of the simulation method used). In some cases, these regions are known; but in most cases, the information about them is missing. The paper gives a description of a global search algorithm for solving such class of problems. Numerical experiments confirming the efficiency of the proposed algorithm were carried out.

\keywords{Lipschitz global optimization \and multiextremal functions \and hidden constraints \and dimensionality reduction.}
\end{abstract}
%
%
%
\section{Introduction}
Global optimization deals with the development of methods for solving problems of finding the global (absolute) minima of multidimensional multiextremal functions. The possibility of constructing a reliable estimate of the global extremum in such problems is principally based on the availability of the \textit{a priori} known information on the problem to be solved. This information makes it possible to relate the unknown values of the objective function to the known values at the points of the performed search trials.

@@

Note that the use of complex mathematical models is natural in the optimization of complex real world objects that, as a consequence, increases the computation costs for searching the optimum Essentially. In last decades, the experts in the fields of optimization and parallel computations have proposed many methods for reducing the computation costs an speed-up of the algorithms related to solving the appearing optimization problems \cite{Kvasov2013}  as well as to the numerical analysis of the original models \cite{Duwe2020}.
